### 2023-02-22 article3.qmd
update

# Case study in the Labrador Sea {#case-study-labrador-sea}

@@

Floats equipped with both a transmissometer and a UVP6 represent an opportunity to look at the influence of parts of the size spectrum on $F_{small}$ and $F_{big}$. For this, we decided to build a regression model using XGBoost, a gradient boosting method [REF], using biovolumes measured by the UVP to predict the slope of $F_{small}$ and $F_{big}$ measured by the OST.

@@

```
```{r, sinking speed values}

@@

J'ai enlevé le truc du spectre inversé à 500 et 1000 m car difficile de conclure -> mais comme on est dans la meme masse d'eau, on pourrait le garder, why not

>>>>

# Case study in the Labrador Sea {#sec-case-study-labrador-sea}

@@

Floats equipped with both a transmissometer and a UVP6 represent an opportunity to look at the influence of parts of the size spectrum on $F_{small}$ and $F_{big}$. For this, we decided to build a regression model using XGBoost, a gradient boosting method \[REF\], using biovolumes measured by the UVP to predict the slope of $F_{small}$ and $F_{big}$ measured by the OST.

@@

```{r, sinking speed values}

@@

J'ai enlevé le truc du spectre inversé à 500 et 1000 m car difficile de conclure -\> mais comme on est dans la meme masse d'eau, on pourrait le garder, why not

### 2023-02-22 intro.qmd
update

So far, we have seen that significant incertitudes remain in the estimations of the carbon export as well as the sequestration time by the different export pathways composing the BCP. To address this issue, biogeochemical models and observation tools are continuously being improved to further our understanding of the BCP (see @sec-modelling-observing-BCP).

>>>>

So far, we have seen that significant incertitudes remain in the estimations of carbon export as well as the sequestration time by the different export pathways composing the BCP. To address this issue, biogeochemical models and observation tools are continuously being improved to further our understanding of the BCP (see @sec-modelling-observing-BCP).

### 2023-02-22 observingCarbonCycle.qmd
update

@Henson2011-mt and @Laws2011-nw (panels a and b in @fig-export-ratios) are both empirical models. @Henson2011-mt parameterized the $e-ratio$ as a decreasing function of SST (derived from satellite observations, see @fig-bgc-models) tuned on a compilation of $^{234}Th$-derived export measurement (see @sec-historical-measurements). They estimated a carbon export of 5 Pg C y$^{-1}$. @Laws2011-nw modelled the $e-ratio$ as a decreasing linear function of SST and a power-law function of NPP whose parameters were determined using particle export estimates based on estimates of new production (nitrogen-based) and $^{234}Th$ and sediment trap export flux data compiled by @Dunne2005-an. They estimated a carbon export of 9 Pg C y$^{-1}$.

@Siegel2014-wg and @Archibald2019-dj (panels c and d in @fig-export-ratios) are both food-web models (see Information Box 3). @Siegel2014-wg used a mechanistic approach using satellite observations (NPP, PSS and phytoplankton carbon concentrations, see also @fig-bgc-models) to estimate the export of the BGP. They estimated a carbon export of 6 Pg C y$^{-1}$. @Archibald2019-dj added a new module to the model of @Siegel2014-wg in order to incorporate the diel vertical migration of zooplankton for a total export of 6.5 Pg C y$^{-1}$.

@@

A simple food-web model is the NPZD model, which consists of four state variables: Nutrient (DIN), Phytoplankton (PHYTO), Zooplankton (ZOO) and DETRITUS. The arrows represent the flows (or interactions) between the state variables (e.g. f1 represents the DIN uptake by PHYTO, f2 represents the grazing of PHYTO by ZOO, etc.), describing the sources and sinks of a given state variable \[@Soetaert2008-er\]. Forcing functions (or external variables) are external factors (i.e. not computed by the model) imposed (i.e. forced) to the model because they drive or regulate the system. Examples of forcing functions (among many others) in ecological models are light intensity (represented here by the solar radiation), temperature or wind. Finally, a model usually contains output variables (represented here by the Chlorophyll) that allow the comparison of the model to reality @Soetaert2008-er.

@@

@DeVries2017-wu and @Nowicki2022-no (panels e and f in @fig-export-ratios) are both data-assimilated models. These models operate by nudging model solutions to the observed fields (e.g. satellite and/or in situ data) or by optimizing model parameters to the observed fields \[@Siegel2022-wd\]. @DeVries2017-wu combined both satellite-derived data (NPP and PSS) and in situ observations (POC fluxes, DOC concentrations and dissolved $O_{2}$ distributions) to assess the carbon export and its transfer in the mesopelagic zone using a steady state ocean circulation inverse model (OCIM, the circulation component of their model). They estimated a carbon export between 7.3 and 8.6 Pg C y$^{-1}$. @Nowicki2022-no added a two-phytoplankton/two-zooplankton food-web model with a migration zooplankton component to the model of @DeVries2017-wu in order to estimate the magnitude of each export pathway of the BCP. In all, @Nowicki2022-no estimated a carbon export of 10 Pg C y$^{-1}$.

@@

Remote sensing data acquired with ocean color satellites have been used for a long time [@Gordon1980-dm] to study key EZ variables related to carbon export [@Claustre2021-tx] such as phytoplankton biomass [@Robinson2004-cj], phytoplankton communities [@Uitz2015-hd] and particle size distribution [@Kostadinov2009-gf; @Kostadinov2010-bu] to name a few (see also @sec-biogeochem-models. While having a wide spatial coverage, these platforms are limited to the ocean's surface and their measures can be affected by several factors such as the cloud cover or low solar elevation (e.g. @Marshall1994-vk).

@@

The BGC-Argo array (@sec-potential-autonomous-platforms) has already demonstrated its ability to understand some aspects of the BCP [e.g. @Lacour2017-ro; @Lacour2019-id; @Briggs2020-gz; @Yang2021-vg; @Llort2018-pa; @Wang2022-hn]. However, the current array may lack some key data to further our understanding of the BCP. Therefore, other types of sensors could be added to BGC-Argo floats to help fill this gap.

décrire les 2 capteurs (pour lesquels je vais m'intéresser) et finir par le projet refine, dire que ça va étudier tel et telle zone, comme cela, ça me fait une rampe de lancement pour le chapitre sur le labrador.

In the frame of the REFINE (Robots Explore plankton-driven Fluxes in the marine twIlight zoNE) project, enhanced BGC-Argo floats (@fig-bgc-float) will have two new sensors specifically designed for the study of the BCP: a transmissometer and the Underwater Vision Profiler 6 (UVP6) [@Picheral2021-sx].

![Illustration of a BGC-Argo float used in the frame of REFINE. From top to bottom: GPS & Iridium (two-way communication) antenna, Oxygen optode, CTD (salinity, temperature and depth), pH sensor, radiometer (downwelling photosynthetic available radiation and downwelling irradiance at 380, 412 and 490 nm), fluorometer (Chla and colored dissolved organic matter) and scattering meter ($b_{bp}$), UVP6 (particle size spectra and images), transmissometer (particle beam attenuation) and nitrate sensor. \@Thomas Boniface.](image/ObservingCarbonCycle/float_picture1.png){#fig-bgc-float width="500"}

@@

The value of $c$ is the result of absorption and scattering by particles, water and dissolved substances [@Zaneveld1994-ez]. The transmissometer carried by REFINE BGC-Argo floats uses a light beam at 660 nm whose attenuation coefficient can be splitted into three components: the absorption and scattering of light by particles ($c_{p}$), the absorption by water ($c_{w}$) and the absorption by dissolved organic matter ($c_{DOM}$) [@Jerlov1976-hr]. At 660 nm, $c_{w}$ is assumed constant at 0.364 m$^{-1}$ and $c_{DOM}$ is considered negligible [@Jerlov1976-hr] hence variations of $c$ will be assumed to be variations of $c_{p}$ in what follows.

The use of transmissometers to characterize POC concentrations was shown by @Bishop1999-es who found that POC concentrations were well correlated with $c_{p}$, independently of ocean environment, season or depth. Following that, the idea of using a transmissometer as an Optical Sediment Trap (OST) was firstly applied by @Bishop2004-at where the magnitude of carbon export was quantified based on the particles accumulation on the upward-facing window of vertically oriented transmissometers on autonomous platforms while they were drifting (i.e. parked at a specific depth). This method was later improved by [@Estapa2013-gw] who divided the attenuation signal into a continuous component, that is the continuous accumulation of small particles on the transmissometer window and a discontinuous component resulting in positive jumps likely attributed to the deposition of (rarer) large particles (@fig-estapa-method). @Estapa2017-jr further calibrated the OST carbon flux proxy using codeployed sediment traps and drifting transmissometers thus allowing the conversion of $c_{p}$ attenuation fluxes (units: m$^{-1}$d$^{-1}$) into carbon fluxes (units: mg C m$^{-2}$d$^{-1}$) using empirical POC-to-attenuance (ATN) ratio were ATN (unitless) is the product of $c_{p}$ and the transmissometer pathlength.

@@

#jump_plot <- ggplot(clean_data, aes(x = dates, y = cp)) + geom_point() + geom_point(data = tmp2, aes(x = dates, y = cp, colour = colour))

# ggplot(despiked_data$data, aes(x = dates, y = cp)) + geom_step(size= 3, fill ='black') + 
#   geom_point(data = tmp2, aes(x = dates, y = cp, colour = colour), size = 3) + 
#   scale_colour_manual(values = c('black','yellow', 'blue')) +
#   theme_bw() +
#   ylab(TeX('$c_{p}~(m^{-1})$')) +
#   xlab('Datetime') +
#   theme(legend.position = c(0.095, 0.875),
#         legend.background = element_rect(fill = "white", color = "black"))

jump <- filter(tmp2, colour == 'jump')

jump_plot <- ggplot(tmp2, aes(x = dates, y = cp, fill = colour)) + geom_point(size= 3) +
  geom_point(data = jump, aes(x = dates, y = cp), size = 3, shape = 21) +
  scale_fill_manual(values = c('#003366','#DCEEF3')) +
  theme_bw() +
  ylab(TeX('$c_{p}~(m^{-1})$')) +
  xlab('Datetime') +
  theme(legend.position = 'top', legend.title = element_blank())

# ggplot(despiked_data$data, aes(x = dates, y = cp)) + geom_point(size= 3, fill ='black') +
#   geom_point(data = jump, aes(x = dates, y = cp), size = 3, shape = 21, fill = '#DCEEF3') +
#   scale_colour_manual(values = c('black','yellow', 'blue')) +
#   theme_bw() +
#   ylab(TeX('$c_{p}~(m^{-1})$')) +
#   xlab('Datetime') +
#   theme(legend.position = 'top')
# 
# jump_plot <- ggplot(base_signal, aes(x = dates, y = cp)) + geom_point(size = 3, shape = 21, fill = '#003366') +
#   geom_point(data = jump, aes(x = dates, y = cp), size = 3, shape = 21, fill = '#DCEEF3') +
#   theme_bw() +
#   ylab(TeX('$c_{p}~(m^{-1})$')) +
#   xlab('Datetime')

#geom_path(data = part_slope, aes(x = time, y = cp, group = group), colour = 'red', size = 2) + theme_bw() + 
#labs(x = 'Time', y = 'Cp (1/m)', title = paste0('Mean slope (red): ', round(mean_slope,3), ' m-1 day-1')) # \n', 'POC flux (small particles): ', poc_flux, 'mg'))

@@

The UVP6 (@fig-UVP6) is a miniaturized version of the UVP5 [@Picheral2021-sx], an imaging system developed to characterize particles (e.g. size, gray level, taxonomic group). Two versions of the UVP6 have been commercialized: the UVP6-HF (high frequency) and the UVP6-LP (low power) which has been specifically designed for AUVs that have strict energy requirements (e.g. autonomous floats).

The UVP6-LP (hereafter referred to as UVP6) is thus both a particle counter (0.1 mm - 2 mm) and a particle classifier (\> 0.6 mm). The former counts particles in different class sizes in order to compute the particle size distribution (PSD) - also referred to as PSS (@sec-BGP) - while the latter extracts pixel-related and geometric features from each image to classify them (i.e. assign them a taxonomic group) directly on board using artificial intelligence (CHAPTER-XX) with the aim of estimating zooplankton biomass [@Claustre2020-jo; @Claustre2021-tx].

@@

While the gathering of data from automatic on board particles classification will have to increase to study related applications, the use of PSD in carbon flux studies has already been thoroughly explored [@Guidi2008-vp; @Iversen2010-an; @Jouandet2011-bt; @McDonnell2012-ic; @Roullier2014-wf; @Guidi2015-sj; @Guidi2016-nj; @Ramondenc2016-nu; @Kiko2017-qy; @Fender2019-ou; @Giering2020-mc; @Cael2021-qn; @Bisson2022-bt].

Using the PSD, one can compute the number spectrum $n_{i}$ [@Stemmann2004-jv] which can be defined as the normalized concentration of particles in a given size bin $i$. Knowing the mass ($m$) and sinking speed ($w$, see @eq-sinking-speed) of aggregates, one can derive the total carbon flux ($F$)

@@

and therefore from @eq-mass-aggregate-fractal and @eq-sinking-speed-fractal that $A= \alpha\beta$ and $D = \frac{B+1}{2}$.

@@

UVP6 PSD measurements will therefore allow the computation of carbon fluxes assuming that $A$ and $B$ are known. This was done empirically by @Guidi2008-vp who minimized the following cost function

@@

In all, it seems that the choice for the values of $A$ and $B$ is critical if one does not want to under- or overestimate carbon fluxes derived from PSD [@Iversen2010-an; @Fender2019-ou]. Three main limitations highlighted by @Bisson2022-bt for UVP optically derived estimates of flux would be: (1) assuming that $A$ and $B$ are globally valid at all depths, for all UVP models and across all size classes, (2) the size to sinking rate uncertainty and (3) the size to carbon mass uncertainty..

@@

## The future of carbon observations {#sec-what-is-next}

The BCP have been studied for many decades by a variety of instruments with their respective pros and cons. Their measurements were unfortunately often taken independently, which hindered their intercomparability due to the low number of concurrent measurements between instruments.

With the advent of fully-equipped AUVs, it is now possible to take high-resolution and independent measurements of key biogeochemical variables. Combining the latter with measurements from conventional platforms (i.e. ships, satellites, moorings) will fulfill the observational framework described by @Claustre2021-tx to investigate the BCP.

This framework will hopefully answer questions raised so far, that is better understand the underlying drivers of each component of the BCP, decouple the contribution of each pump to the observed downward carbon flux lengthily attributed to the BGP and better quantify global estimates of carbon storage.

@@

<!-- The quantification of the different carbon export pathways of the BCP and the fate of the exported carbon in the mesopelagic zone are among the hardest problems in modern oceanography [@Siegel2016-kh; @Le_Moigne2019-zl] but also the most pressuring issues in the context of climate change [@Martin2020-wa]. If the BCP is not responsible for the absorption of anthropogenic $CO_{2}$, any changes in its strength or efficiency could greatly impact atmospheric $CO_{2}$ concentrations [@Kwon2009-ir]. Thus, there is a need to better understand the biological and physical drivers of each component of the BCP, estimate the amount of carbon they export to the deep ocean and their sequestration potential. -->

<!-- To this aim, a new observational framework has been proposed by @Claustre2021-tx to combine measurements from several observations platforms (i.e. research vessels, satellites, moorings and automated underwater vehicles (AUVs)). New sensors have been developed for AUVs (see section @sec-BGC-sensors) in order to better characterize the type of particles (e.g. zooplankton, fecal pellets, aggregates), their size and their mechanisms of transformation (e.g. fragmentation, aggregation). Combining independent measurements of specific biogeochemical variables will allow to tackle the double accounting problem, that is the issue of distinguishing particles associated with the BGP and a PIP, therefore potentially attributing the transport of a particle to more than one pump [@Boyd2019-ez]. This is of particular importance to better constrain the contribution of each PIP to carbon storage in the global ocean [@Boyd2019-ez]. -->

<!-- In addition, the refinement of the contribution of each PIP would both help to close the ocean carbon budget [@Burd2010-hc] and improve estimates of carbon sequestration [@Boyd2019-ez; @Passow2012-zh] that will enhance the evaluation of the efficiency of carbon dioxide removal strategies [@Siegel2022-wd]. -->

<!-- Based on that, the objectives of this work are threefold: -->

1.  <!-- Contribute to the development of new sensors for AUVs, namely the development of the zooplankton embedded recognition algorithm for the Underwater Vision Profiler 6 [@Picheral2021-sx], an imaging system that will be used to characterize particles > 600 $\mu$m. -->

2.  <!-- Exploit the synergy of instruments on fully-equipped profiling floats in a specific region (Labrador Sea) to shed a light on mesopelagic processes that affect the size and sinking speed of aggregates as well as characterizing the downward flux of small and big particles and its variability. -->

3.  <!-- Reassess the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth. -->

>>>>

@Henson2011-mt and @Laws2011-nw (panels a and b in @fig-export-ratios) are both empirical models. @Henson2011-mt parameterized the $e-ratio$ as a decreasing function of SST (derived from satellite observations, see @fig-bgc-models) tuned on a compilation of $^{234}Th$-derived export measurement (see @sec-historical-measurements) for a total export estimated at 5 Pg C y$^{-1}$. @Laws2011-nw modelled the $e-ratio$ as a decreasing linear function of SST and a power-law function of NPP whose parameters were determined using particle export estimates based on estimates of new production (nitrogen-based) and $^{234}Th$ and sediment trap export flux data compiled by @Dunne2005-an. They estimated a total export of 9 Pg C y$^{-1}$.

@Siegel2014-wg and @Archibald2019-dj (panels c and d in @fig-export-ratios) are both food-web models (see Information Box 3). @Siegel2014-wg used a mechanistic approach using satellite observations (NPP, PSS and phytoplankton carbon concentrations, see also @fig-bgc-models) to estimate the export of the BGP (6 Pg C y$^{-1}$). @Archibald2019-dj added a new module to the model of @Siegel2014-wg in order to incorporate the diel vertical migration of zooplankton for a total export of 6.5 Pg C y$^{-1}$.

@@

A simple food-web model is the NPZD model, which consists of four state variables: Nutrient (DIN), Phytoplankton (PHYTO), Zooplankton (ZOO) and DETRITUS. The arrows represent the flows (or interactions) between the state variables (e.g. f1 represents the DIN uptake by PHYTO, f2 represents the grazing of PHYTO by ZOO, etc.), describing the sources and sinks of a given state variable [@Soetaert2008-er]. Forcing functions (or external variables) are external factors (i.e. not computed by the model) imposed (i.e. forced) to the model because they drive or regulate the system. Examples of forcing functions (among many others) in ecological models are light intensity (represented here by the solar radiation), temperature or wind. Finally, a model usually contains output variables (represented here by the Chlorophyll) that allow the comparison of the model to reality @Soetaert2008-er.

@@

@DeVries2017-wu and @Nowicki2022-no (panels e and f in @fig-export-ratios) are both data-assimilated models. These models operate by nudging model solutions to the observed fields (e.g. satellite and/or in situ data) or by optimizing model parameters to the observed fields [@Siegel2022-wd]. @DeVries2017-wu combined both satellite-derived data (NPP and PSS) and in situ observations (POC fluxes, DOC concentrations and dissolved $O_{2}$ distributions) to assess the carbon export and its transfer in the mesopelagic zone using a steady state ocean circulation inverse model (OCIM, the circulation component of their model). Their carbon export estimate is between 7.3 and 8.6 Pg C y$^{-1}$. @Nowicki2022-no added a two-phytoplankton/two-zooplankton food-web model with a migration zooplankton component to the model of @DeVries2017-wu in order to estimate the magnitude of each export pathway of the BCP. In all, @Nowicki2022-no estimated a carbon export of 10 Pg C y$^{-1}$.

@@

Remote sensing data acquired with ocean color satellites have been used for a long time [@Gordon1980-dm] to study key EZ variables related to carbon export [@Claustre2021-tx] such as phytoplankton biomass [@Robinson2004-cj], phytoplankton communities [@Uitz2015-hd] and particle size distribution [@Kostadinov2009-gf; @Kostadinov2010-bu] to name a few (see also @sec-biogeochem-models). While having a wide spatial coverage, these platforms are limited to the ocean's surface and their measures can be affected by several factors such as the cloud cover or low solar elevation (e.g. @Marshall1994-vk).

@@

The BGC-Argo array (@sec-potential-autonomous-platforms) has already demonstrated its ability to understand some aspects of the BCP [e.g. @Lacour2017-ro; @Lacour2019-id; @Briggs2020-gz; @Yang2021-vg; @Llort2018-pa; @Wang2022-hn]. However, the current array may lack some key data to further our understanding of the BCP. Therefore, other types of sensors could be added to help fill this gap.

In this work, I will focus on two sensors: a transmissometer used as an optical sediment trap (OST) and the Underwater Vision Profiler 6 (UVP6) [@Picheral2021-sx], a miniaturized version of the UVP5 (@fig-bgc-float).

![Illustration of an augmented BGC-Argo float. From top to bottom: GPS & Iridium (two-way communication) antenna, Oxygen optode, CTD (salinity, temperature and depth), pH sensor, radiometer (downwelling photosynthetic available radiation and downwelling irradiance at 380, 412 and 490 nm), fluorometer (Chla and colored dissolved organic matter) and scattering meter ($b_{bp}$), UVP6 (particle size spectra and images), transmissometer (particle beam attenuation) and nitrate sensor. \@Thomas Boniface.](image/ObservingCarbonCycle/float_picture1.png){#fig-bgc-float width="400"}

@@

The value of $c$ is the result of absorption and scattering by particles, water and dissolved substances [@Zaneveld1994-ez]. The transmissometer uses a light beam at 660 nm whose attenuation coefficient can be splitted into three components: the absorption and scattering of light by particles ($c_{p}$), the absorption by water ($c_{w}$) and the absorption by dissolved organic matter ($c_{DOM}$) [@Jerlov1976-hr]. At 660 nm, $c_{w}$ is assumed constant at 0.364 m$^{-1}$ and $c_{DOM}$ is considered negligible [@Jerlov1976-hr] hence variations of $c$ essentially represent variations of $c_{p}$.

The use of transmissometers to characterize POC concentrations was shown by @Bishop1999-es who found that POC concentrations were well correlated with $c_{p}$, independently of ocean environment, season or depth. Subsequently, the idea of using a transmissometer as an OST was firstly applied by @Bishop2004-at where the magnitude of carbon export was quantified based on the particles accumulation on the upward-facing window of vertically oriented transmissometers on autonomous floats while they were drifting (i.e. parked at a specific depth). This method was later improved by [@Estapa2013-gw] who divided the attenuation signal into a continuous component, that is the regular accumulation of small particles on the transmissometer window and a discontinuous component resulting in positive jumps likely attributed to the deposition of (rarer) large particles (see @fig-estapa-method and @sec-case-study-labrador-sea). @Estapa2017-jr further calibrated the OST carbon flux proxy using codeployed sediment traps and drifting transmissometers thus allowing the conversion of $c_{p}$ attenuation fluxes (units: m$^{-1}$d$^{-1}$) into carbon fluxes (units: mg C m$^{-2}$d$^{-1}$) using empirical POC-to-attenuance (ATN) ratio were ATN (unitless) is the product of $c_{p}$ and the transmissometer pathlength.

@@

# change names
tmp2 <- tmp2 |> mutate(colour = if_else(colour == 'cleaned signal', 'Small particle deposition', 'Big particle deposition (jump)'))

jump <- filter(tmp2, colour == 'Big particle deposition (jump)')

jump_plot <- ggplot(tmp2, aes(x = dates, y = cp, fill = colour)) + geom_point(size= 3) +
  geom_point(data = jump, aes(x = dates, y = cp), size = 3, shape = 21) +
  #scale_fill_manual(values = c('#003366','#DCEEF3')) +
  scale_fill_manual(values = c('#DCEEF3', '#003366')) +
  theme_bw() +
  ylab(TeX('$c_{p}~(m^{-1})$')) +
  xlab('Datetime') +
  theme(legend.position = 'top', legend.title = element_blank())

@@

The UVP6 (@fig-UVP6) is a miniaturized version of the UVP5 [@Picheral2021-sx], an imaging system developed to characterize particles (e.g. size, gray level, taxonomic group). Two versions of the UVP6 are available: the UVP6-HF (high frequency) and the UVP6-LP (low power) which has been specifically designed for AUVs that have strict energy requirements (e.g. autonomous floats).

The UVP6-LP (hereafter referred to as UVP6) is thus both a particle counter (0.1 mm - 2 mm) and a particle classifier (\> 0.6 mm). The former counts particles in different class sizes in order to compute the PSD while the latter extracts pixel-related and geometric features from each image to classify them (i.e. assign them a taxonomic group) directly on board using artificial intelligence (@sec-uvp-ia) with the aim of estimating zooplankton biomass [@Claustre2020-jo; @Claustre2021-tx].

@@

The deployment of autonomous platforms equipped with a UVP6 and the zooplankton recognition algorithm for the study of the BCP is just beginning (first deployment in May 2022 in the Labrador Sea, see @sec-case-study-labrador-sea). On the contrary, the use of PSD in carbon flux studies has already been thoroughly explored [@Guidi2008-vp; @Iversen2010-an; @Jouandet2011-bt; @McDonnell2012-ic; @Roullier2014-wf; @Guidi2015-sj; @Guidi2016-nj; @Ramondenc2016-nu; @Kiko2017-qy; @Fender2019-ou; @Giering2020-mc; @Cael2021-qn; @Bisson2022-bt].

Using the PSD, one can compute the number spectrum $n_{i}$ [@Stemmann2004-jv] which can be defined as the normalized concentration of particles in a given size bin $i$. Knowing the mass ($m$) and sinking speed ($w$, see @eq-sinking-speed) of aggregates, one can derive the total mass flux ($F$)

@@

and therefore from @eq-mass-aggregate-fractal and @eq-sinking-speed-fractal that $A= \alpha\beta$ and $B = 2D-1$.

@@

@Guidi2008-vp used POC fluxes derived from sediment traps and UVP PSD data to estimate the $A$ and $b$ values of @eq-carbon-flux-finite by minimizing the following cost function

@@

In all, it seems that the choice for the values of $A$ and $B$ is critical for deriving carbon fluxes derived from PSD [@Iversen2010-an; @Fender2019-ou]. Three main limitations highlighted by @Bisson2022-bt for UVP optically derived estimates of flux would be: (1) assuming that $A$ and $B$ are globally valid at all depths, for all UVP models and across all size classes, (2) the size to sinking rate uncertainty and (3) the size to carbon mass uncertainty..

@@

@@

In the context of the pressing issue of climate change, better understanding the BCP is of paramount importance [@Martin2020-wa]. Although the BCP is not responsible for the absorption of anthropogenic $CO_{2}$, any change in its strength or efficiency could have a significant impact on atmospheric $CO_{2}$ concentrations [@Kwon2009-ir]. Therefore, there is a need to better understand the biological and physical drivers of each component of the BCP to reduce uncertainties in the amount of carbon exported and its sequestration potential.

To this end, a new observational framework has been proposed by @Claustre2021-tx to combine measurements from several platforms (i.e. research vessels, satellites, moorings and AUVs) to investigate the BCP. Within this framework, AUVs are being deployed with newly developed sensors to characterize the type of sinking particles (e.g. zooplankton, fecal pellets, aggregates), their size and the transformation mechanisms affecting them (e.g. fragmentation, aggregation).

This framework will hopefully address the questions raised so far, i.e., better understand the underlying drivers of each component of the BCP, decouple the contribution of each pump to the observed downward carbon flux lengthily attributed to the BGP and estimates of carbon sequestration \[@Boyd2019-ez; @Passow2012-zh\] as well as close the ocean carbon budget \[@Burd2010-hc\].

This work will therefore address three mains topics related to the study of the BCP:

1.  BGC-Argo floats equipped with a UVP6 and the zooplankton recognition algorithm are able to classify particles larger than 0.6 mm. However, these AUVs are limited in terms of their battery life. They are typically deployed for several years, which requires special attention to the energy consumption of each sensor. In @sec-uvp-ia I will therefore describe the methodology used to develop the zooplankton classification model for the UVP6 accounting for energy limitations.
2.  4 BGC-Argo floats equipped with both a transmissometer and a UVP6 were deployed for the first time in the Labrador Sea in late May 2022 to investigate the post-spring bloom and its associated POC fluxes. In @sec-case-study-labrador-sea, I will show how transmissometers used as OSTs compare with PSDs measured by UVP6s as well as investigate the link between small and big particle fluxes derived by both instruments.
3.  Many studies have assumed that carbon sequestration only occurs in the deep ocean (typically 1000 m). In @sec-to-do, I reassess the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.
